Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-04-20 paper/ms.tex
abstract rewritten

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and  occupation fraction ($f_{\rm occ}$) of
dark matter halos hosting \ly\ Emitting  Galaxies ((LAEs) at high redshift. 
We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.  
In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\mathrm h}<M_{\rm   max}$ can only host one detectable LAE at most. By following a Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ . 
However, the current observational data only allows us to put weak constraints on $M_{\rm min}$ and consequently on $f_{\rm occ}$. Particularly, we find that $10^{9.6}\hMsun\leq M_{\rm min}\leq 10^{11.0}\hMsun$ , $10^{10.9}\hMsun\leq M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\leq f_{\rm occ}\leq 0.30$. 
Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width of the distribution  of the	  LAE number density obtained over several fields of the same size of current observations.  Analogously, the  improvement in the precision of the measured ACF will assist in constraining $M_{\rm max}$.  
\end{abstract}

>>>>

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
We construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAEat most.    
We explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using as observational
constraints the angular correlation function (ACF) and the LAEs number density. 
We find that the preferred minium and maximum masses in our model span
a wide range $10^{9.6}\hMsun\leq \mmin \leq 10^{11.0}\hMsun$ ,
$10^{10.9}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all models consistent with
observations has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun, in agreement with the most recent
observational estimates.
However, we find that the same individual models have a relatively tight
mass gap, $\Delta M \equiv \log_{10}\mmax - \log_{10}\mmin$, of $\Delta
M\approx 0.3$dex.
We are also able show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$, by
$\focc\sim0.1(\mmin/10^{10.5}\hMsun )^{0.93}$.  
However, the current observational data only allows us to put weak
constraints on \mmin\ and consequently on \focc.
We show that upcoming large surveys covering at least $50$ deg$^{2}$
will be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$ using the relationship, $W_{1\sigma} =
0.138\times (\mmin/10^{11}\hMsun )^{0.177}$, calibrated from our results.
\end{abstract}
